Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

%%%%%%%%%%%% 
\subsection{Model Set-up}\label{section:results:setup}
Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}. This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014,jackson_2015,salinas2015,pavlidis2016}.

\medskip
In this work, all test-cases were performed in idealised geometries discretised with unstructured triangular and tetrahedral mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs (Fig.~\ref{fig:fem_elem}). An implicit Crank-Nicolson time-stepping scheme was used with {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy condition \citep[CFL,][]{courant_1941} of 2. In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$. For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varied in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$. Fluids are assumed incompressible and gravity was neglected. The set-up for the numerical simulations are summarised in Table \ref{table:setup}.

>>>>

%%%%%%%%%%%% 
\subsection{Model Set-up}\label{section:results:setup}
Numerical simulations were conducted with the model summarised in Section \ref{equations_scheme} and embedded in the next-generation reservoir simulator Fluidity/IC-FERST model software\footnote{\href{http://multifluids.github.io}{http://multifluids.github.io}} \citep[a full description of the model can be found in][]{porosity_documentation,fluidity_manual,jackson_2013,gomes_2017}. This multi-physics model has been validated against traditional multi-fluids test-cases (\eg advection-diffusion, Buckley-Leverett problem, channel model, immiscible displacement, gravity-driven displacement etc) in \citet{radunz_2014}, \citet{jackson_2015}, \citet{salinas2015} and \citet{pavlidis2016}.

\medskip
In this work, all test-cases were performed in idealised geometries discretised with unstructured triangular and tetrahedral mesh using the \PN[1]{2} and \PN[1]{1} FE-pairs (Fig.~\ref{fig:fem_elem}). An implicit Crank-Nicolson time-stepping scheme was used with {\it a posteriori} adaptive time-step size targeting a maximum Courant-Friedrichs-Lewy condition \citep[CFL,][]{courant_1941} of 2. In most simulations, the domain was initially fully saturated with non-wetting fluid which was displaced by a pure (wetting) fluid at a prescribed initial velocity $\left(u^{0}\right)$. For simplicity, the porosity ($\phi$) of the domain was kept constant at 0.2 in all simulations, whereas the absolute permeability ($\mathbf{K}$) varied in space, \ie $\mathbf{K}=\mathbf{K}\left(x_{i}\right)$. Fluids are assumed incompressible and gravity was neglected. Initial set-up for the numerical simulations is summarised in Table \ref{table:setup}.
